---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hw6sparsevec

<!-- badges: start -->
[![R-CMD-check](https://github.com/cartoful97/hw6sparsevec/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/cartoful97/hw6sparsevec/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of hw6sparsevec is to represent a sparse vector with many 0s in a more 
 efficient form than simply as a dense vector, by storing only the positions and
 corresponding values of nonzero elements. 

## Installation

You can install the development version of hw6sparsevec by cloning the GitHub
 repository to your computer, then running `devtools::install("hw6sparsevec")` 
 in the R console.

## Class

The class has 3 attributes: a numeric vector containing the nonzero values of 
 the sparse vector, an integer vector containing the positions of the sparse 
 vector, and the integer length of the complete sparse vector, including 0s.
 You can initialize a sparse numeric object as follows:

```{r}
library(hw6sparsevec)

x <- new("sparse_numeric",
         value = c(1, 2, 1),
         pos = c(1L, 2L, 5L),
         length = 5L)
x
```

Or, you can convert a numeric vector to a sparse numeric object:

```{r}
x <- as(c(0, 0, 0, 1, 2), "sparse_numeric")
x
```

## Functions

The functions `sparse_add()`, `sparse_mult()`, and `sparse_sub()` perform their 
 respective operations on two sparse numeric vector objects.
 
```{r}
x <- as(c(-2, 8, 3, 0, 1), "sparse_numeric")
y <- as(c(2, 0, 7, 1, -9), "sparse_numeric")
print('addition')
sparse_add(x, y)
print('subtraction')
sparse_sub(x, y)
print('multiplication')
sparse_mult(x, y)
```

Instead of using the functions directly, the numerical symbols of +, -, and * can 
 be used as well.

```{r}
print('addition')
x + y
print('subtraction')
x - y
print('multiplication')
x * y
```

The function `sparse_crossprod()` calculates the cross product of two sparse
 numeric vectors (the sum of the vectors multiplied together).
 
```{r}
sparse_crossprod(x, y)
```

The function `unsparse()` removes all zeros from a sparse numeric and returns the
 result as a numeric vector.
 
```{r}
x
unsparse(x)
```
The `plot` function plots the values of elements with overlapping positions of
 nonzero elements between two sparse numerics.
 
```{r}
plot(x, y)
```

The function `mean()` finds the mean of the elements of a sparse numeric vector.

```{r}
x
mean(x)
```
The function `norm()` finds the squared norm of the vector (the square root of 
 the sum of the squared elements).

```{r}
x
norm(x)
```
The function `standardize()` standardizes the elements of the sparse vector and 
 returns the result as a dense vector, as all the standardized 0s are unlikely 
 to remain 0.
 
```{r}
x
standardize(x)
```





